Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-12 article.tex
Changes @Giappo

The pipeline is summarized by the following steps:
\begin{enumerate}
  \item from a given phylogeny an alignment is simulated 
    under a known alignment model;
  \item from this alignment, according to the specified inference conditions, 
    an inference model is picked (which may differ from the 
    generative alignment model);
  \item the alignment and inference model are used 
    to infer a posterior distribution;
  \item the phylogenies in the posterior are compared with the given phylogeny 
    to estimate the error made, according to the error measure specified 
    by the user;
\end{enumerate}
The pipeline is visualized in Fig.~\ref{fig:pipeline}. 
There is also the option to generate a 'twin tree', 
that goes through the same pipeline. 
The utility of this twin tree will be explained below.

>>>>

The pipeline is summarized by the following steps:
\begin{enumerate}
  \item from a given phylogeny an alignment is simulated 
    under a known alignment model $\mathit{A}$;
  \item from this alignment, according to the specified inference conditions $\mathit{C}$, 
    an inference model $\mathit{I}$ is picked (which may differ from the 
    generative alignment model);
  \item the alignment and inference model are used 
    to infer a posterior distribution;
  \item the phylogenies in the posterior are compared with the given phylogeny 
    to estimate the error made, according to the error measure $\mathit{E}$ specified 
    by the user;
\end{enumerate}
The pipeline is visualized in Fig.~\ref{fig:pipeline}. 
There is also the option to generate a 'twin tree', 
that goes through the same pipeline. 
The utility of this twin tree will be explained below.
